---
output:
  tufte::tufte_handout: default
  #tufte::tufte_html: default
params:
  
  file: x
  title: y
#title : "Test" 
title: "`r  params$title`"
header-includes:
  - \usepackage{float}
---

```{r, echo = FALSE, message=FALSE}
library(tidyverse)
library(ggpubr)
library(ggpmisc)
library(ggExtra)
library(openxlsx)
library(RcppRoll)
library(kableExtra)

data <- read.csv(file, header = TRUE)

#data <- read.csv("Toronto_60410_2018/Toronto_60410_2018_Day10to16.csv", header = TRUE)
```


```{r, echo = FALSE}
#data <- read.csv(params$file, header = TRUE)


data <- data %>%
  mutate(time = convertToDateTime(data$Date, origin = "1900-01-01")) %>%
  filter(O3 != -999) %>%
  filter(NO2 != -999) %>%
  mutate(OX = NO2 + O3)

### Making data tidyR friendly --------------------------------------------------
dataCol <- data %>%
  select(-c("Date")) %>%
  pivot_longer(-time, names_to = "pollutant", values_to = "concentration")
### -----------------------------------------------------------------------------



```


The results below are what the student results should look like for the `r  params$title` dataset used in CHM 135 Experiment 1.

```{r, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE, fig.height = 3.5, fig.cap= "(A) Time series of pollutant concentration. There shouldn't be a linear regression on this plot, if students have done so please note it. (B) Correlation plot of O3 vs. NO2; the equation of the line is displayed in the lower left corner. "}


### Time series plot of NO2, O3, and OX ------------------------------------------
a <- ggplot(data = dataCol, aes(x = time, y = concentration, color = pollutant)) +
  geom_line(size = 1) +
  theme_classic() +
   theme(text = element_text(size = 10),
         legend.position = "right") +
  ylab(bquote('Conc., ppb')) +
  xlab(bquote('Time')) 
### -----------------------------------------------------------------------------

formula <- y ~ x ### Need to keep this so LM regression appears on plot

### Correlation plot with Linear regression and equation -------------------------
b <- ggplot(data = data, aes(x = NO2, y = O3)) +
  geom_point(size = 0.5) + 
  scale_x_continuous(expand = c(0, 0), limits = c(0, NA)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_classic() +
  theme(text = element_text(size = 10))+
  xlab(bquote('Conc.' ~NO[2]~', ppb')) +
  ylab(bquote('Conc.' ~O[3]~', ppb')) +
  geom_smooth(method = "lm", formula = formula, se = FALSE) +
  stat_poly_eq(aes(label =  paste(stat(eq.label), stat(rr.label), sep = "*\", \"*")),
               formula = formula, rr.digits = 4 , parse = TRUE, label.y = 0.05, size = 3)

#b

ggarrange(a,b, nrow = 2, labels = c("A","B"))

```


```{r, echo = FALSE, warning = FALSE, message = FALSE, error = FALSE}

### 8hr rolling average data for table
data$NO2_8hr <- roll_mean(data$NO2, 7, na.rm = TRUE, fill = NA, align = 'right')
data$O3_8hr  <- roll_mean(data$O3, 7, na.rm = TRUE, fill = NA, align = 'right')
data$OX_8hr  <- roll_mean(data$OX, 7, na.rm = TRUE, fill = NA, align = 'right')

data8hrCol <- data %>%
  select(c("time", "NO2_8hr", "O3_8hr", "OX_8hr")) %>%
  pivot_longer(-time, names_to = "pollutant", values_to = "meanConc_8hr") %>%
  filter(!is.na(meanConc_8hr))
### ------------------------------------------------------------------------------



### Summary Stats for 1hr and 8 hr pollutant concentrations ------------------------------
stable <- desc_statby(dataCol, measure.var = "concentration", grps = "pollutant") %>%
  select(c("pollutant", "mean", "sd", "median", "min", "max"))

stable8hr <- desc_statby(data8hrCol, measure.var = "meanConc_8hr", grps = "pollutant")%>%
  select(c("pollutant", "mean", "sd", "median", "min", "max"))


stableAll <- rbind(stable, stable8hr)


knitr::kable(stableAll, 
             align = "lrrrrr",
             caption = "Summary statistics for 1 hr and 8hr concentration of pollutants, all concentrations are in ppb.",
             digits = c(0,1,1,0,0,0),
             format = "latex",
             booktabs = T
            ) 



```


## Notes on results: 

Students are **not** expected to calculate *mean*, *sd*, and *median* of 8 hr averages. If student *sd* values differ slightly from provided *sd* values, they may have used the *STDEV.P* funcation rather than *STDEV.S* in Excel calculations. Do not substract points, but make a note of it.


