---
output:
  tufte::tufte_handout: default
  #tufte::tufte_html: default
params:
  
  file: x
  title: y
#title : "Test" 
title: "`r  params$title`"
header-includes:
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, warning = FALSE, message = FALSE)
```

  
```{r packages}
library(tidyverse) # ggplot, readr, etc. 
library(ggpubr) # ggarrange for plots
library(ggpmisc) # for displaying equation on plot
library(RcppRoll) # for rolling averages
library(kableExtra) # outputting summary table

data <- read_csv(file, locale = readr::locale(encoding = "Latin1"))

# used to test .rmd file
# data <- read_csv("Toronto,ON_60435_2018/Toronto_60435_2018_Day180to186.csv", 
#                  locale = readr::locale(encoding = "Latin1"))
```


```{r, echo = FALSE}
#data <- read.csv(params$file, header = TRUE)

# Converting Excel dates to POSIX
if(is.numeric(data$Time[[1]])){
  
  data <- data %>%
    mutate(Time = as.POSIXct(Time*3600*24 , origin="1899-12-30", tz="GMT"))
  
}

data <- data %>%
  filter(O3 != -999) %>%
  filter(NO2 != -999) %>%
  mutate(OX = NO2 + O3)

# Making data tidyR friendly ----
dataCol <- data %>%
  pivot_longer(-c(Time, NAPS), names_to = "Pollutant", values_to = "Concentration")

```


The results below are what the student results should look like for the `r  params$title` dataset used in CHM 135 Experiment 1.

```{r plots, , fig.height = 3.5, fig.cap= "(A) Time series of pollutant concentration. There shouldn't be a linear regression on this plot, if students have done so please note it. (B) Correlation plot of O3 vs. NO2; the equation of the line is displayed in the lower left corner. "}


### Time series plot of NO2, O3, and OX ------------------------------------------
a <- ggplot(data = dataCol, aes(x = Time, y = Concentration, color = Pollutant)) +
  geom_line(size = 1) +
  theme_classic() +
  theme(text = element_text(size = 10),
        legend.position = "right") +
  ylab(bquote('Conc., ppb')) +
  xlab(bquote('Time')) 
### -----------------------------------------------------------------------------

formula <- y ~ x ### Need to keep this so LM regression appears on plot

### Correlation plot with Linear regression and equation -------------------------
b <- ggplot(data = data, aes(x = NO2, y = O3)) +
  geom_point(size = 0.5) + 
  scale_x_continuous(expand = c(0, 0), limits = c(0, NA)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, NA)) +
  theme_classic() +
  theme(text = element_text(size = 10))+
  xlab(bquote('Conc.' ~NO[2]~', ppb')) +
  ylab(bquote('Conc.' ~O[3]~', ppb')) +
  geom_smooth(method = "lm", formula = formula, se = FALSE) +
  ggpmisc::stat_poly_eq(aes(label =  paste(stat(eq.label), stat(rr.label), sep = "*\", \"*")),
               formula = formula, rr.digits = 4 , parse = TRUE, label.y = 0.05, size = 3)

#b

ggpubr::ggarrange(a,b, nrow = 2, labels = c("A","B"))

```


```{r summary-table}

### 8hr rolling average data for table
data$NO2_8hr <- RcppRoll::roll_mean(data$NO2, 7, na.rm = TRUE, fill = NA, align = 'right')
data$O3_8hr  <- RcppRoll::roll_mean(data$O3, 7, na.rm = TRUE, fill = NA, align = 'right')
data$OX_8hr  <- RcppRoll::roll_mean(data$OX, 7, na.rm = TRUE, fill = NA, align = 'right')

data8hrCol <- data %>%
  select(c("Time", "NO2_8hr", "O3_8hr", "OX_8hr")) %>%
  pivot_longer(-Time, names_to = "Pollutant", values_to = "meanConc_8hr") %>%
  filter(!is.na(meanConc_8hr))
### ------------------------------------------------------------------------------



### Summary Stats for 1hr and 8 hr pollutant concentrations ------------------------------
stable <- ggpubr::desc_statby(dataCol, measure.var = "Concentration", grps = "Pollutant") %>%
  select(c("Pollutant", "mean", "sd", "median", "min", "max"))

stable8hr <- ggpubr::desc_statby(data8hrCol, measure.var = "meanConc_8hr", grps = "Pollutant")%>%
  select(c("Pollutant", "mean", "sd", "median", "min", "max"))


stableAll <- rbind(stable, stable8hr)


knitr::kable(stableAll, 
             align = "lrrrrr",
             caption = "Summary statistics for 1 hr and 8hr concentration of pollutants, all concentrations are in ppb.",
             digits = c(0,1,1,0,0,0),
             format = "latex",
             booktabs = T
) 



```


## Notes on results: 

Students are **not** expected to calculate *mean*, *sd*, and *median* of 8 hr averages. If student *sd* values differ slightly from provided *sd* values, they may have used the *STDEV.P* function rather than *STDEV.S* in Excel calculations. Do not substract points, but make a note of it.


