---
title: "CTFP Final Report"
subtitle: "Excel-erating Data Analysis Skills in an Introductory Chemistry Lab"
author: "David Hall and Dr. J. D'eon (supervisor)"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
```

# Introduction

* data analysis 
  + import -> .csv to .xlsx
  + tidy -> remove -999, view Dates, remove gaps in data
  + transform -> OX calculation, summary statistics, potential for 8hr rolling average
  + visualize -> time series and correlation plots
  + communicate -> questions students awnsered. 

# Source of Data

* ECCC online
  + hourly measurements
* Weather Data

# Operations in Excel 

* tried a bunch of stuff, and left plenty on the cutting room floor
  + SO2 work 
  + using Analysis Toolpak for linear regression (outputs additional parameters hidden from display line of best fit)
  
Eventually settled on comparing time series & correlations between summer and winter months. Addressed the 5 elements of data analysis highlited in the intro:

  * import -> .csv to .xlsx
  * tidy -> remove -999, view Dates, remove gaps in data
  * transform -> OX calculation, summary statistics, potential for 8hr rolling average
  * visualize -> time series and correlation plots
  * communicate -> questions students awnsered. 

# Logistics

Had to genereate unique data for students, and had to be expandable. 
*run through the r code process highlighting stuff like generating datasets & awnser keys* 

# Troubles with implementation

Only uploaded 15 winter and 15 summer datasets. Unfamiliarity & Disconnect between me and Quercus/Teaching Staff hampered some of the broader implementations. 


```{r bib, include=FALSE}
# create a bib file for the R packages used in this document
knitr::write_bib(c('base', 'rmarkdown'), file = 'skeleton.bib')
```
